\addchap{Acknowledgements}

% 主査
First and foremost, I would like to express my sincere gratitude to my
supervisor Professor Shinji Shimojo at the Cybermedia Center, Osaka
University. He continuously and convincingly conveyed a spirit of adventure
and excitement to this study. His excellent advices based on his deep
knowledge always provided a unique perspective and new meaning to this study.

% 副査
I would like to thank Professor Makoto Onizuka and Professor Yasuyuki
Matsushita at the Department of Multimedia Engineering, the Graduate School of
Information Science and Technology, Osaka University for serving as
dissertation committee members and providing me valuable advice and guidance
throughout my doctoral research work.

% 専攻の教授
Sincere thanks also goes to Professor Takahiro Hara, Professor Toru Fujiwara,
and Professor Norihiro Hagita at the Department of Multimedia Engineering,
the Graduate School of Information Science and Technology, Osaka University
for their appropriate guidance.

% 指導教員
I would like to express my deepest appreciation to Associate Professor Susumu
Date at the Cybermedia Center, Osaka University, for his patient and
enthusiastic guidance along my studies. His exceptional ability to analyze,
solve and present scientific problems has constantly impressed me. Without his
support and encouragement, this dissertation would not have been possible.

% NICTプロジェクト
I also would like to thank Dr.~Eiji Kawai and Dr.~Hiroaki Yamanaka at the
National Institute of Information and Communications Technology, Associate
Professor Hirotake Abe at the University of Tsukuba, Associate Professor Kohei
Ichikawa at the Nara Institute of Science and Technology, Associate Professor
Yoshiyuki Kido and Specially Appointed Associate Professor Yasuhiro Watashiba
at the Cybermedia Center, Osaka University, for their encouragement,
insightful comments, and hard questions.

% ヒューマンウェアイノベーションプログラム
I am grateful to Specially Appointed Associate Professor Kazufumi Hosoda and
Specially Appointed Associate Professor Suyong Eum at the Institute for
Transdisciplinary Graduate Degree Programs, Osaka University, who always
showed me daring ideas and unique approaches to look at a problem through
discussions. I also would like to express my gratitude to the student advisory
committee members of the Humanware Innovation Program, particularly Kaoru
Amano at the National Institute of Information and Communications Technology,
and Akira Sakakibara at Microsoft Japan, for their invaluable feedbacks. This
research was supported in part by the scholarship and research funding
provided by the Humanware Innovation Program.

% 兼任教員
This study greatly benefited from the comments and advices from Associate
Professor Kazuhide Kojima at the Cybermedia Center, Osaka University,
Professor Kaname Harumoto at the Institute for Datability Science, Osaka
University, Associate Professor Hiroki Kashiwazaki, Guest Professor Takashi
Yoshikawa, and Specially Appointed Associate Professor Chonho Lee at the
Cybermedia Center, Osaka University. Their suggestions improved the quality of
this thesis much further.

% 学生
I would like to thank all the students at Shimojo laboratory for the sleepless
nights we worked together before deadlines, and for all the fun we had. It was
a great pleasure working with you all.

% 家族
I would like express my heartfelt gratitude to my parents, Toshihito Takahashi
and Naoko Takahashi, for their continuous support, encouragement and care. They
made me the person who I am today.

Finally, but most importantly, I would like to express my deepest gratitude
and appreciation to my wife Ziyan Xu for her unconditional love and support
throughout my studies and my personal life.
