\chapter{Conclusion}\label{sec:v}

\section{Concluding Remark}
% 問題
The inter-process communication of applications running on cluster systems
show distinctive patterns. However, in contrast to the application-dependent
communication pattern, the interconnect is inherently designed in an
application-agnostic manner because a real-world cluster is usually shared by
many users and each user runs various applications. As a result,
the imbalance in the packet flow on the interconnect can take place under
particular combinations of communication pattern and interconnect. This
imbalance can lead to traffic congestion on links in the interconnect, which
lowers the throughput of communication and degrades the total application
performance as a result.

% 目的
This dissertation tackled this imbalance problem by taking the strategy of
adapting the interconnect to the communication pattern of applications.
Traditionally, such dynamic adaptation of the interconnect has been deemed
infeasible due to the lack of a networking architecture, technology, or
technique that allows flexible and dynamic reconfiguration. However, the
recent emergence of programmable networking architectures exemplified by
Software-Defined Networking~(SDN) has opened up the possibility to realize
such adaptation. This dissertation aimed to overcome this shortcoming of
conventional application-agnostic interconnects by establishing a programmable
interconnect control that dynamically controls the packet flow in the
interconnect based on the communication pattern of applications.

% 課題
The following three challenges have been tackled to achieve the goal described
above: (1)~analyzing the packet flow in the interconnect, (2)~accelerating MPI
communication by dynamically controlling the packet flow in the interconnect,
and (3)~coordinating the execution of application and interconnect control.

% 提案1
To address the first challenge, Chapter~\ref{sec:ii} proposed PFAnalyzer, a
toolset for analyzing the packet flow in the interconnect. When designing and
implementing an efficient programmable interconnect control, researchers need
to conduct a systematic analysis over many combinations of applications and
interconnects. Since performing such an analysis on a physical cluster is
time-consuming, this dissertation has chosen the strategy of using simulation
to facilitate the analysis. The proposed toolset is a pair of tools: an
interconnect simulator specialized for programmable interconnects, and a
profiler to collect communication pattern from applications. PFSim has allowed
researchers and designers working on interconnects to investigate possible
congestion in the interconnect for an arbitrary cluster configuration and a
set of communication patterns extracted by PFProf. In the evaluation, the
accuracy of the simulation results obtained from PFSim was assessed.
Furthermore, how PFAnalyzer can be used to analyze the effect of programmable
interconnect control was demonstrated.

% 提案2
To address the second challenge, Chapter~\ref{sec:iii} proposed a framework to
accelerate MPI collectives by dynamically controlling the packet flow in the
interconnect. Message Passing Interface~(MPI) is a standardized inter-process
communication library widely used to develop parallel distributed
applications for clusters. Out of the communication primitives provided by
MPI, this dissertation focused on accelerating collective communication
because it usually occupies a significant fraction of the execution time of
applications. The network programmability provided by Software-Defined
Networking was integrated into MPI collectives in such a way that MPI
collectives were able to effectively utilize the bandwidth of the
interconnect. In particular, this dissertation aimed to reduce the execution
time of MPI\_Allreduce, which is a frequently used MPI collective
communication in many simulation codes. The speedup of MPI\_Allreduce when
using the proposed collective acceleration framework was evaluated.

% 提案3
To address the third challenge, Chapter~\ref{sec:iv} proposed UnisonFlow, a
software-defined coordination mechanism that performs interconnect control in
synchronization with the execution of applications. In real-world
applications, the communication pattern changes with the execution of
application. For the reason, a mechanism to coordinate packet flow control and
execution of application is essential for the adaptation of the interconnect to
the time-varying communication pattern of real-world applications. UnisonFlow
was proposed as a kernel-assisted mechanism that realizes such coordination on
a per-packet basis while maintaining significantly low overhead. Evaluation
shown in Chapter~\ref{sec:iv} verified that the interconnect control was
successfully performed in synchronization with the execution of the
application and the overhead imposed by the coordination mechanism was small.

\section{Future Work}

% 複数ジョブへの対応
In this dissertation, it was assumed that only a single job is executed on the
cluster. However, a production cluster usually executes multiple jobs
simultaneously. Therefore, the proposed programmable interconnect control
should be enhanced to support multiple concurrent jobs on a cluster. This
enhancement is a challenging task because of the following two reasons. First,
the interconnect control needs to be coordinated with the scheduling of jobs.
In other words, the interconnect control needs to be triggered each time a job
starts and a job exits. Such coordination could be realized by integrating the
job scheduler with the interconnect controller. Second, inter-job interference
of packet flow needs to be considered. The coexistence of multiple jobs on a
single cluster implies that the packet flow generated by different jobs may
share a single link. Under such situation, the packet flow generated by a
communication-intensive job could occupy the interconnect and degrade the
communication performance of other jobs. In fact, researchers have reported a
significant performance variability of jobs on production clusters caused by
the interference of packet flow between different jobs~\cite{Bhatele2013}.
Therefore, the programmable interconnect control should globally optimize the
packet flow in the interconnect while considering the communication pattern of
each job and the interference between jobs, so that all jobs can equally
benefit from the interconnect control.

% スケーラビリティ
Due to the limited scale of the cluster that was available for the
experiments, the scalability of the proposed programmable interconnect control
has not been thoroughly investigated yet. There are mainly two challenges in
applying the programmable interconnect control to large-scale clusters
composing of large number of compute nodes. The first challenge is the
concentration of load on the interconnect controller. As described in
Section~\ref{sec:i-sdn}, a centralized controller oversees the entire network
in SDN\@. This design inherently poses a limit in the scale of the cluster
since the work that needs to be performed by the controller, such as
monitoring the state of the interconnect and exchanging control messages with
the switches, dramatically increases with the number of compute nodes in the
cluster. To overcome this limitation, multi-controller
architecture~\cite{Hu2018} may be utilized. Under the multi-controller
architecture, the network is managed by multiple controllers working
cooperatively. The second challenge is the limit of flow entries that a switch
can handle. The number of flow entries that need to be installed on each
switch increases rapidly with the number of compute nodes composing the
cluster.  However, the number of flow entries that can be stored in the TCAM
of an SDN switch is limited. This problem might be solved by merging redundant
flow entries or evicting flow entries from switches that are rarely matched.
